\Title

### 2021-06-25 manuscript/content.tex
Minor corrections to the text
Clarify that we mean "overly large and small" values. Remove the colon and 
start a new sentence.

\noindent where
$\mathbf{W}$ is a $N \times N$ diagonal matrix of data weights and
$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
Jacobian matrix elements.
The second term on the right-hand side of the equation is a zeroth-order
Tikhonov regularization \citep{tikhonov1977} (also known as a damping
regularization or ridge regression) that is used to stabilize the solution.
The damping parameter controls the amount of regularization that will be applied:
a large damping value would generate smooth solutions that fail to reproduce
the high frequency components, while a small value would overfit the data,
failing to produce realistic interpolation results \citep{martinez2016}.

>>>>

\noindent where
$\mathbf{W}$ is a $N \times N$ diagonal matrix of data weights and
$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
Jacobian matrix elements.
The second term on the right-hand side of the equation is a zeroth-order
Tikhonov regularization \citep{tikhonov1977} (also known as a damping
regularization or ridge regression) that is used to stabilize the solution.
The damping parameter controls the amount of regularization that will be applied.
An overly large value would generate a smooth solution that fails to reproduce
the high frequency components of the data, while an overly small value would 
result in over-fitting, thus failing to produce realistic interpolation results 
\citep{martinez2016}.
